Classless Java

### 2015-11-15 paper/sections/RelatedWork.tex
Some more work on last part of related work

\subsection{Type-Directed Translations/Syntactic Sugar}
Language extensions are often implemented as syntactic sugar of the base
language. For example, Scala compiler supports XML syntax in normal Scala code
directly (after Scala ?, users need to import \texttt{scala-xml} library
manually). However, this approach is hard in terms of implementation, because it
requires extending the compiler. Also, this approach does not support combining
multiple extensions into one.

@@

\subsection{Meta-programming techniques}
- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}

>>>>

\subsection{Type-Directed Translations/Syntactic Sugar}
\marco{I'm tring to merge this and the next one}
Language extensions are often implemented as syntactic sugar of the base
language. For example, Scala compiler supports XML syntax in normal Scala code
directly (after Scala ?, users need to import \texttt{scala-xml} library
manually). However, this approach is hard in terms of implementation, because it
requires extending the compiler. Also, this approach does not support combining
multiple extensions into one.

@@

\subsection{Meta-programming competes with Language extensions}
The most obvious solution to add features to a language, is language extension.
They are often implemented as syntactic sugar of the base
language. For example, the Scala compiler was extended to directly supports XML syntax. However, this approach does not support combining multiple extensions into one. We are de facto creating a fork in the language, and rarely the new fork gain enough traction to become the main language release.
On this topic we mention SugarJ~\cite{erdweg11sugarj}; a Java-based extensible language allowing programmers to extend it with custom features by definitions in meta-DSLs (SDF, Stratego, etc).

On the other side, when the starting language have a flexible enough syntax and a fast and powerful enough reflection, we may just need to play with operator overloading and other language tricks to discover that the language feature we need can be expressed a a simple library in our language. For example, consider SQL alchemy in python.

Java-like language tends to sits in the middle of this two extremes:
libraries can not influence the type system, so many solutions valid in python or other languages could not be applicable, or may be applicable at the cost of loosing safety.

- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}
